Quality assurance of digital twins -- An experience report in the automotive industry

### 2023-02-11 manuscripts/paper-1/main.tex
Simulation quality added

    \subsection{Product quality and Management}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
    Regarding product quality, there are two different aspects~\cite{GrievesPLMBook}.
    First, quality is an attribute of a product, which meets product specifications. Specifications are mostly defined by the supra-systems subsystems, such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
    The ability to execute to a specific usage standard is the second facet of product quality. Since this standardization is usually not controllable, unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.

@@

    \subsection{Software quality}
    Software is a  virtual system, which has a set of instructions, data or programs used to perform a specific task. 
    All virtual systems, which we described above, need a medium to live on, hence these systems can be found in a computer or other electronic device.  
    Software quality according to IEEE 730-2014, is: 
    `The degree to which a software product meets established requirements; however, 
    quality depends upon the degree to which those established requirements accurately represent stakeholder needs, wants, and expectations'~\cite{IEE730-2014}. 
    As can be seen, it's a generic explanation of a quality, which doesn't differ much from the explanation we gave above.

    Software quality management techniques come from already used manufacturing techniques in the industries.
    For example, the quality assurance which we mentioned above, also has been used as a software quality management activity with some differences. 
    In manufacturing, products will never exactly meet a specification, due to errors in the machining so there should be some tolerance for the manufacturing. 
    But in the software systems, or more precisely in the virtual systems, it's most of the time, not the case. 
    Also its nearly impossible to conclude that, the software product fully meets its specifications\cite{SoftwareEngineering}.

@@

    \subsection{Digital twin quality}
    To analyze current DT literature within the concept of digital twin quality literature analysis was executed. 
    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations.

@@

    Important findings are the following;

    \begin{itemize}
        \item Shcherba et al. center their attention on the model quality, which is an observation for a digital twin subsystem. Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin.
        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al. and can be used to assess the quality of the models. Additionally, the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models. The improvement of the service component is the primary emphasis of this article. Tao's five-dimensional digital twin concept includes this component.
        \item He Zhang et al. introduce the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed.
        \item Selch et al. work is the only one that discusses the quality of the digital twin. The paper presents a machine-learning approach based on Bayesian networks to track the quality of the digital twin. The unique aspect of this study is that the author, rather than just analyzing the digital twin as a single system, determines the contributions of subsystems to forecast the overall quality of the digital twin. The digital couplings, which are linkages between the subsystems, are also mentioned by Selch et al. as a source of extra uncertainty. 
        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated.
    \end{itemize}

@@

    \subsection{First criterion: Correctness}

    \subsubsection{Definition}
    Car vs airplane (with nice pictures!)

>>>>

    \subsection*{Product quality and Management}
    A product is a tangible or intangible system that satisfies the needs or wants of a customer. It could be a physical system like a car, or an abstract system, like a digital twin. 
    Regarding product quality, there are two different aspects~\cite{GrievesPLMBook}.
    First, quality is an attribute of a product, which meets product specifications. Specifications are mostly defined by the supra-systems subsystems, such as by the stakeholders within the supra-system,  If the stakeholders' expectations, or needs, are met, we can consider high quality.
    The ability to execute to a specific usage standard is the second facet of product quality. Since this standardization is usually not controllable, unlike the first, the system's quality will be determined by how the implied or obligatory standards are fulfilled.

@@

    \subsection*{Software quality}
    Software is a  virtual system, which has a set of instructions, data or programs used to perform a specific task. 
    All virtual systems, which we described above, need a medium to live on, hence these systems can be found in a computer or other electronic device.  
    Software quality according to IEEE 730-2014, is: 
    `The degree to which a software product meets established requirements; however, 
    quality depends upon the degree to which those established requirements accurately represent stakeholder needs, wants, and expectations'~\cite{IEE730-2014}. 
    As can be seen, it's a generic explanation of a quality, which doesn't differ much from the explanation we gave above.

    Software quality management techniques come from already used manufacturing techniques in the industries.
    For example, the quality assurance that we mentioned above, also has been used as a software quality management activity with some differences. 
    In manufacturing, products will never exactly meet a specification, due to errors in the machining so there should be some tolerance for the manufacturing. 
    But in the software systems, or more precisely in the virtual systems, it's most of the time, not the case. 
    Also its nearly impossible to conclude that, the software product fully meets its specifications\cite{SoftwareEngineering}.

@@

    \subsection*{Simulation Quality}
    Simulation models are not merely virtual systems; they are also abstracted systems, which are nothing more than imitations or, to be more precise, abstractions of real systems. 
    We are simulating every day when we are trying to predict the future outcome or abstractly thinking about the past state of some occurred event. 
    An important element to remember is that we mentally model the event before executing the simulation. However, most of the simulation processes we see today, 
    are computer-based, with software programs. These programs include ANSYS\cite{Ansys}, ABAQUS\cite{Abaqus}, and AnyLogic\cite{AnyLogic}, as examples. Consequently, the idea of simulation software programs emerges.

    Validation and verification can be used to evaluate the quality characteristics of the simulation model \cite{StewartSimulation} \cite{VerificationValidationSergent} \cite{OsmanBalci}. 
    Validation is the process of evaluating the simulation quality of the model in comparison to the real system from the perspective of the model's intended applications. 
    On the other hand, verification is a procedure to evaluate a simulation model's implementation and its associated data concerning the conceptual description and specifications of the model developer.

    \subsection*{Digital twin quality}
    To analyze current DT literature within the concept of digital twin quality literature analysis was executed. 
    The analysis especially focused on how the digital twin quality is mentioned and assessed within the academic dissertations.

@@

    Important findings are the following;
    \begin{itemize}
        \item Shcherba et al. center their attention on the model quality, which is an observation for a digital twin subsystem. Despite being a crucial component of the digital twin, models alone cannot be used to assess the quality of the digital twin.
        \item A consistency evaluation approach for digital twin models was developed by He Zhang et al. and can be used to assess the quality of the models. Additionally, the authors discuss crucial ideas like consistency between real and virtual systems and ultra-fidelity models. The improvement of the service component is the primary emphasis of this article. Tao's five-dimensional digital twin concept includes this component.
        \item He Zhang et al. introduces the updating method for digital twin models in yet another insightful article. Once more, the accuracy and coherence of the model concepts were addressed.
        \item Selch et al. work is the only one that discusses the quality of the digital twin. The paper presents a machine-learning approach based on Bayesian networks to track the quality of the digital twin. The unique aspect of this study is that the author, rather than just analyzing the digital twin as a single system, determines the contributions of subsystems to forecast the overall quality of the digital twin. The digital couplings, which are linkages between the subsystems, are also mentioned by Selch et al. as a source of extra uncertainty. 
        Since only one digital twin has been used in practice, multiple subsystem digital twins have not been validated.
    \end{itemize}

@@

    \subsection{First criterion: Correctness}
    \subsubsection{Definition}
    Correctness, 
    Car vs airplane (with nice pictures!)
